WIDS 2024 Final Project

### 2024-01-09 Code/R FIle.qmd
more graphs. better code

```{r}
library(tidyverse)
```

@@

##### For facets, use best judgement if by state, decade, year, or region

##### maybe make all states light grey and just choose outline outlier states and maybe regional averages

@@

```{r}
ggplot(full_state_data, aes(x = state_abbreviation, y = )) +
```

@@

```{r}
effective_min_wage_adj_graph1 <- full_state_data |> 
  filter(!is.na(regions)) |> 
  filter(effective_min_wage_2020_adj != fed_min_wage_2020_adj) |> 
  filter(state_abbreviation != "HI") |> 
  ggplot(aes(x = year)) +
  geom_line(aes(y = effective_min_wage_2020_adj, color = state_abbreviation)) +
  scale_color_manual(values = c(rep("gray", 34))) +
  geom_line(aes(y = fed_min_wage), color = "red", linewidth = .75)

HI_effective_min_wage <- full_state_data |> 
  filter(!is.na(regions)) |> 
  filter(effective_min_wage_2020_adj != fed_min_wage_2020_adj) |> 
  filter(state_abbreviation == "HI") |> 
  mutate(effective_min_wage_2020_adj = effective_min_wage_2020_adj - .05)

CT_effective_min_wage <- full_state_data |> 
  filter(!is.na(regions)) |> 
  filter(effective_min_wage_2020_adj != fed_min_wage_2020_adj) |> 
  filter(state_abbreviation == "CT")

AK_effective_min_wage <- full_state_data |> 
  filter(!is.na(regions)) |> 
  filter(effective_min_wage_2020_adj != fed_min_wage_2020_adj) |> 
  filter(state_abbreviation == "AK")

CA_effective_min_wage <- full_state_data |> 
  filter(!is.na(regions)) |> 
  filter(effective_min_wage_2020_adj != fed_min_wage_2020_adj) |> 
  filter(state_abbreviation == "CA")

effective_min_wage_adj_graph1 +
  geom_line(data = HI_effective_min_wage, aes(y = effective_min_wage_2020_adj), color = "blue",linewidth = .7) +
  annotate("text", x=1994, y=9.5, label= "Hawaii", color = "blue") +
  geom_line(data = CT_effective_min_wage, aes(y = effective_min_wage_2020_adj), color = "#288225", linewidth = .7) +
  annotate("text", x=1985, y=7.5, label= "Connecticut", color = "#288225") +
  geom_line(data = AK_effective_min_wage, aes(y = effective_min_wage_2020_adj), color = "orange", linewidth = .7) +
  annotate("text", x=1985, y=10, label= "Alaska", color = "orange") +
  geom_line(data = CA_effective_min_wage, aes(y = effective_min_wage_2020_adj), color = "purple", linewidth = .7) +
  annotate("text", x=2016, y=12, label= "California", color = "purple") +
  annotate("text", x=2000, y=5.5, label= "Federal", color = "red") +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "State effective minimum wage by Year (adjusted for 2020 $)",
       subtitle = "For states with an adjusted effective minimum wage above the federal level",
       x = "Year",
       y = "Effective minimum wage (2020 USD)")

rm(HI_effective_min_wage, CT_effective_min_wage,
   AK_effective_min_wage, CA_effective_min_wage)
```

@@

>>>>

```{r}
library(tidyverse)
library(usmap)
```

@@

* For facets, use best judgement if by state, decade, year, or region

* maybe make all states light grey and just choose outline outlier states and maybe regional averages

@@

```{r}
library(gganimate)
library(gifski)
library(transformr)
```

```{r}
map_data <- full_state_data |> 
  select(c("year", "state", "state_abbreviation", "party_state_avaerage")) |> 
  distinct(year, state, .keep_all = TRUE) |> 
  filter(year %% 4==0) |> 
  filter(!is.na(party_state_avaerage))

plot_usmap(data = map_data, values = "party_state_avaerage", color = "black") +
  facet_wrap(~year, nrow = 2, ncol= 6) +
  theme(legend.position = "top") +
  scale_fill_gradient(low = "red", high = "blue")
```

@@

```{r}
state_minimum_wage_data <- full_state_data |> 
  filter(!is.na(regions)) |>
  filter(year <=2020 ) |> 
  mutate(
    map_color = case_when(
      state_abbreviation == "CA" ~ "CA",
      state_abbreviation == "AK" ~ "AK",
      state_abbreviation == "OK" ~ "OK",
      state_abbreviation == "FL" ~ "FL",
      .default = NA
    )
  ) 
state_minimum_wage_data |> 
  ggplot(aes(x = year)) +
  geom_line(aes(y = state_min_wage_2020_adj, group = state_abbreviation),
            color = "grey75", alpha =0.6) +
  geom_line(data = subset(state_minimum_wage_data, !is.na(map_color)),
            aes(y = state_min_wage_2020_adj, color = map_color),
            linewidth = .75) +
  geom_line(aes(y = fed_min_wage), color = "red", linewidth = .75) +
  theme_minimal() +
  labs(title = "State Minimum Wage by Year (Adjusted for 2020 $)",
       subtitle = "For states with an adjusted effective minimum wage above the federal level",
       x = "Year",
       y = "Minimum wage (2020 USD)")
```

@@

```{r}
effective_minimum_wage_data <- full_state_data |> 
  filter(!is.na(regions)) |> 
  filter(effective_min_wage_2020_adj != fed_min_wage_2020_adj) |> 
  mutate(
    map_color = case_when(
      state_abbreviation == "CA" ~ "CA",
      state_abbreviation == "AK" ~ "AK",
      state_abbreviation == "CT" ~ "CT",
      state_abbreviation == "HI" ~ "HI",
      .default = NA
    )
  ) 
effective_minimum_wage_data |> 
  ggplot(aes(x = year)) +
  geom_line(aes(y = effective_min_wage_2020_adj, group = state_abbreviation),
            color = "grey75", alpha =0.6) +
  geom_line(data = subset(effective_minimum_wage_data, !is.na(map_color)),
            aes(y = effective_min_wage_2020_adj, color = map_color),
            linewidth = .75) +
  geom_line(aes(y = fed_min_wage), color = "red", linewidth = .75) +
  theme_minimal() +
  labs(title = "State Effective Minimum Wage by Year (Adjusted for 2020 $)",
       subtitle = "For states with an adjusted effective minimum wage above the federal level",
       x = "Year",
       y = "Effective minimum wage (2020 USD)")
```
